Optimal (Multiway) Spatial Joins

### 2024-05-31 msj.tex
yufei

When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a containment query on $\T$ to find all the intervals in $S_\ell$ that are contained by $[z_1, z_2]$; if $K_h$ is the number of such intervals, this retrieval takes $O(\log n + K_h)$ time. For each retrieved interval $[x_1, x_2]$, we also obtain its host rectangle $r$ (stored along with $[x_1, x_2]$ in $\T$). Observe that $h$ is the lowest segment in $H$ that crosses $r$. We store $h$ in the cell of array $A$ allocated to $r$ and then mark $r$ as inactive; accordingly, we remove $[x_1, x_2]$ from $T$ in $O(\log n)$ time. As $r$ will remain inactive in the rest of the execution, its x-range $[x_1, x_2]$ will not be retrieved by another containment query in the future.

@@

Overall, each rectangle of $R$ necessitates one insertion and one deletion in $\T$. All these insertions and deletions take $O(n \log n)$ time in total. Each segment $h$ of $H$ performs a query on $\T$, which has a cost of $O(\log n + K_h)$. All these queries demand a total cost of $O(n \log n + \sum_h K_h)$. Recall that the x-range of a rectangle in $R$ can be retrieved by at most one query. Hence, $\sum_h K_h \le n$ and the runtime of our algorithm is $O(n \log n)$.

>>>>

When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a containment query on $\T$ to find all the intervals in $S_\ell$ that are contained by $[z_1, z_2]$; if $K_h$ is the number of such intervals, this retrieval takes $O(\log n + K_h)$ time. For each retrieved interval $[x_1, x_2]$, we also obtain its host rectangle $r$ (stored along with $[x_1, x_2]$ in $\T$). Observe that $h$ is the lowest segment in $H$ that crosses $r$. We store $h$ in the cell of array $A$ allocated to $r$, after which $r$ is marked as inactive, and accordingly, its x-range $[x_1, x_2]$ is deleted from $T$ in $O(\log n)$ time. As $r$ will remain inactive in the rest of the execution, its x-range will not be retrieved again by another containment query in the future.

@@

Overall, each rectangle of $R$ necessitates one insertion and one deletion in $\T$. All these insertions and deletions take $O(n \log n)$ time in total. Each segment $h$ of $H$ performs a containment query on $\T$, which has a cost of $O(\log n + K_h)$. All these queries demand a total cost of $O(n \log n + \sum_h K_h)$. Recall that the x-range of a rectangle in $R$ can be retrieved by at most one containment query. Hence, $\sum_h K_h \le n$ and the runtime of our algorithm is $O(n \log n)$.
